Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-30 WSSSPE3/report/WSSSPE3_review.tex
adding DASPOS references/cites

\item \textbf{Mike Hildreth, Jarek Nabrzyski, Da Huo, Peter Ivie, Haiyan Meng,
Douglas Thain, and Charles Vardeman: \textit{Data And Software Preservation for
Open Science (DASPOS)}}. DASPOS is an NSF-funded multi-disciplinary effort,
located at Notre Dame and Chicago, that links the high energy physics effort to
other disciplines such as biology, astrophysics, and digital curation. It includes
physicists, digital librarians, as well as computer scientists, and aims to
achieve some commonality across disciplines. Examples are meta-data descriptions
of archived data, computational descriptions, descriptions of how data was
processed, questions such as whether computation replication can be automated,
and what the impact of access policies on the preservation infrastructure is.
One of the products of this effort is a suite of tools that deals with this
preservation, and the questions was posed whether that software itself is
sustainable. Points that were brought up included the need for a user community
depending on a given software, and the need to provide added value for its
users. An important method to achieve this was to work with the user community
from the start, and to budget that way. For the specific example of the
preservation software, this means that besides adding value to the community, it
needs to be transparent to their workflows, i.e., not requiring additional
effort to preserve ``research objects.''

>>>>

\item \textbf{Mike Hildreth, Jarek Nabrzyski, Da Huo, Peter Ivie, Haiyan Meng,
Douglas Thain, and Charles Vardeman: \textit{Data And Software Preservation for
Open Science (DASPOS)}}. DASPOS\footnote{\url{http://daspos.org}} is an NSF-funded multi-disciplinary effort,
located at Notre Dame and Chicago, that links the high energy physics effort to
other disciplines such as biology, astrophysics, and digital curation. It includes
physicists, digital librarians, as well as computer scientists, and aims to
achieve some commonality across disciplines. Examples are meta-data descriptions
of archived data, computational descriptions, descriptions of how data was
processed, questions such as whether computation replication can be automated,
and what the impact of access policies on the preservation infrastructure is.
One of the products of this effort is a suite of tools that deals with this
preservation~\cite{Meng2015137,Meng:2015:UPE:2755979.2755982,1742-6596-664-3-032022,nd4},
and the questions was posed whether that software itself is
sustainable. Points that were brought up included the need for a user community
depending on a given software, and the need to provide added value for its
users. An important method to achieve this was to work with the user community
from the start, and to budget that way. For the specific example of the
preservation software, this means that besides adding value to the community, it
needs to be transparent to their workflows, i.e., not requiring additional
effort to preserve ``research objects.''
